---
title: "ASSESSING THE IMPACT OF MOTHER’S PERCEPTION OF SUPPORT ON BREASTFEEDING INTENSITY THROUGH SIX MONTHS: STATISTICAL ANALYSIS"
author: "KATIE PALOMARES"
output:
  pdf_document:
    toc: yes
    toc_depth: 5
  html_document:
    toc: yes
    toc_depth: '5'
    df_print: paged
---

\newpage

## Data Prep

The code shown below implements the following process:

1. Read in full IFPS dataset
2. Subset the dataset to fields relevant to the study and apply necessary transformations
3. Fit a multinomial logistic regression model to the data in order to ascertain the significance
of perception of support on breast feeding intensity.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(
    # This should allow Rmarkdown to locate the data
    root.dir = rprojroot::find_rstudio_root_file()
)

library(haven)
library(data.table)
library(magrittr)
library(stats)
library(nnet)
library(lmtest)
library(MASS)
library(ggplot2)
library(googledrive)
library(pedometrics)
library(car)
```

```{r data_prep, results = 'hide', echo = TRUE}


data.directory <- file.path(rprojroot::find_rstudio_root_file(), "0_Data")
project.directory <- rprojroot::find_rstudio_root_file()
ifps_dt <- "ifps2.sas7bdat" %>%
           file.path(data.directory, .) %>%
           read_sas() %>%
           as.data.table()


ifps_subset_dt <- ifps_dt[, .(SAMPMIQ)]

####################################################################
#DATA TRANSFORMATIONS
####################################################################
# Breastfeeding difficulties, question 36 --------------------------

N36_cols <- colnames(ifps_dt)[colnames(ifps_dt) %like% "N36"]

N36_dt <- melt(ifps_dt[, .SD, .SDcols = c("SAMPMIQ", N36_cols)], 
                id.vars = "SAMPMIQ", 
                value.name = "response", 
                variable.name = "question")

N36_dt %<>% .[, .(response = sum(response, na.rm = TRUE)), keyby = .(SAMPMIQ)]

N36_dt[, breast_feeding_difficulties := FALSE]
N36_dt[response > 0, breast_feeding_difficulties := TRUE]

ifps_subset_dt[N36_dt, 
        breast_feeding_difficulties := i.breast_feeding_difficulties, 
        on = .(SAMPMIQ)]

rm(N36_dt, N36_cols)

# ----------------------------------------------------------------------

# Breast feeding support, question 38 -----------------------------------

N38_dt <- ifps_dt[, .(N38, SAMPMIQ)]
N38_dt[, breast_feeding_support := FALSE]
N38_dt[N38 == 1, breast_feeding_support := TRUE]

ifps_subset_dt[N38_dt, 
            breast_feeding_support := i.breast_feeding_support, 
            on = .(SAMPMIQ)]

rm(N38_dt)

# ------------------------------------------------------------------------

# Perception of support, question 39

N39_dt <- ifps_dt[, .(N39, SAMPMIQ)]

N39_dt[N39 %in% c(1, 2), perception_of_support := "Unhelfpul"]
N39_dt[N39 %in% c(3), perception_of_support := "Inconclusive"]
N39_dt[N39 %in% c(4, 5), perception_of_support := "Helpful"]

ifps_subset_dt[N39_dt, 
            perception_of_support := i.perception_of_support, 
            on = .(SAMPMIQ)]

rm(N39_dt)

# -----------------------------------------------------------------------

# Breast Feeding Intensity at 2 - 6 months ----------------------------

months <- 1:6

for(i in months){

  if (i == 1) {
    feeding_cols <- colnames(ifps_dt)[colnames(ifps_dt) %like% "N40"]
    
    bf_feeding_col <- "N40A"
  } else {
    feeding_cols <- paste0("M", i, "A1", LETTERS[1:10])
    
    bf_feeding_col <- paste0("M", i, "A1A")
  }

  
  temp_dt <- melt(ifps_dt[, .SD, .SDcols = c("SAMPMIQ", feeding_cols)],
                  id.vars = "SAMPMIQ",
                  value.name = "response",
                  variable.name = "question")
  
  temp_dt[is.na(response) & question == bf_feeding_col, response := 0]
  
  temp_dt %<>% .[, .(breast_feeding_intensity = response[question == bf_feeding_col]/sum(response, 
                                                                                     na.rm = TRUE)), 
                keyby = .(SAMPMIQ)]
  
  temp_dt[is.nan(breast_feeding_intensity), breast_feeding_intensity := NA]
  
  ifps_subset_dt[temp_dt, 
                 breast_feeding_intensity := i.breast_feeding_intensity, 
                 on = .(SAMPMIQ)]
  
  setnames(ifps_subset_dt, 
           "breast_feeding_intensity", 
           paste0("breast_feeding_intensity_", i, "_mo"))
  
  rm(feeding_cols, bf_feeding_col, temp_dt)
}

# ----------------------------------------------------------------------

# BFHI Exposure --------------------------------------------------------

BFHI_dt <- ifps_dt[, .SD, .SDcols = c("N20", 
                                      "N11", 
                                      "N25", 
                                      "N28", 
                                      paste0("N29", c("A", "B", "C")),
                                      "N32", 
                                      "SAMPMIQ")]

number_BFHI_criteria <- 6

# Time until mother breastfed for the first time
BFHI_dt[N20 %in% 1:2, BFHI_exp_1 := TRUE]
BFHI_dt[N20 %in% 3:9, BFHI_exp_1 := FALSE]

# No Pacifiers
BFHI_dt[N11 %in% c(1, 3), BFHI_exp_2 := FALSE]
BFHI_dt[N11 %in% c(2), BFHI_exp_2 := TRUE]

# Rooming in
BFHI_dt[N25 %in% c(1), BFHI_exp_3 := TRUE]
BFHI_dt[N25 %in% c(2, 3), BFHI_exp_3 := FALSE]

# BF on Demand
BFHI_dt[N28 %in% c(1), BFHI_exp_4 := TRUE]
BFHI_dt[N28 %in% c(2, 3), BFHI_exp_4 := FALSE]

# Only BM
BFHI_dt[N29A == 2 & N29B == 2 & N29C == 2, BFHI_exp_5 := TRUE]
BFHI_dt[N29A %in% c(1, 3) | N29B %in% c(1, 3) | N29C %in% c(1, 3), 
        BFHI_exp_5 := FALSE]

# Fostering support groups
BFHI_dt[N32 == 1, BFHI_exp_6 := TRUE]
BFHI_dt[N32 == 2, BFHI_exp_6 := FALSE]

BFHI_dt %<>% melt(., measure.vars = paste0("BFHI_exp_", 1:number_BFHI_criteria),
                  variable.name = "question",
                  value.name = "response")

BFHI_dt %<>% .[, .(BFHI_score = sum(response, na.rm = TRUE),
                   BFHI_all_missing = all(is.na(response))), by = .(SAMPMIQ)]

BFHI_dt[BFHI_all_missing == TRUE, BFHI_score := NA]

ifps_subset_dt[BFHI_dt, BFHI_score := i.BFHI_score, on = .(SAMPMIQ)]

rm(BFHI_dt, number_BFHI_criteria)
# ----------------------------------------------------------------------

# Maternal Age ---------------------------------------------------------
P9_dt <- ifps_dt[, .(P9, SAMPMIQ)]

P9_dt[, unique(P9)] %>% sort()

P9_dt[, maternal_age := cut(P9, 
                            breaks = c(18, 25, 30, 35, Inf), 
                            labels = c("18-24", "25-29", "30-34", "35+"),
                            include.lowest = TRUE,
                            right = FALSE)]

ifps_subset_dt[P9_dt, maternal_age := i.maternal_age, on = .(SAMPMIQ)]

rm(P9_dt)
# ----------------------------------------------------------------------

# Race/Ethnicity -------------------------------------------------------

race_dt <- ifps_dt[, .(RACE_ETH, SAMPMIQ)]

race_dt[RACE_ETH == 1, race_eth := "White, Non-Hispanic"]
race_dt[RACE_ETH == 2, race_eth := "Black, Non-Hispanic"]
race_dt[RACE_ETH == 3, race_eth := "Hispanic"]
race_dt[RACE_ETH %in% c(4, 5), race_eth := "Other"]

ifps_subset_dt[race_dt, race_eth := i.race_eth, on = .(SAMPMIQ)]

rm(race_dt)
# ----------------------------------------------------------------------

# Education ---------------------------------------------
edu_dt <- ifps_dt[, .(EDUC, SAMPMIQ)]

edu_dt[EDUC %in% c(1, 2, 3), education := "Less Than High School"]
edu_dt[EDUC %in% c(4), education := "High School"]
edu_dt[EDUC %in% c(5), education := "1-3 Years College"]
edu_dt[EDUC %in% c(6, 7), education := "College Graduate"]

ifps_subset_dt[edu_dt, education := i.education, on = .(SAMPMIQ)]

rm(edu_dt)
# -------------------------------------------------------

# Parity ------------------------------------------------
parity_dt <- ifps_dt[, .(P41_1, P41_2, SAMPMIQ)]

parity_dt[P41_1 == 0 & P41_2 == 0, parity := "nullipara"]
parity_dt[P41_1 %in% 1:12 | P41_2 %in% 1:12, parity := "primipara"]

ifps_subset_dt[parity_dt, parity := i.parity, on = .(SAMPMIQ)]

parity_dt[, .N, by = .(keyby = P41_1)]
parity_dt[, .N, by = .(keyby = P41_2)]
rm(parity_dt)
# -------------------------------------------------------

# Income Level --------------------------------------------

income_dt <- ifps_dt[, .(INCOME, SAMPMIQ)]

income_dt[INCOME %in% 31:37, income := "<$20,000"]
income_dt[INCOME %in% 38:46, income := "$20,000-$49,999"]
income_dt[INCOME %in% 47:57, income := ">$50,000"]

ifps_subset_dt[income_dt, income := i.income, on = .(SAMPMIQ)]

rm(income_dt)
# ---------------------------------------------------------

# BMI -----------------------------------------------------
bmi_dt <- ifps_dt[, .(P7, P8FT, P8IN, SAMPMIQ)]

bmi_dt[, bmi := (P7/((P8FT * 12 + P8IN)^2)) * 703]

bmi_dt[bmi < 18.5, bmi_class := "Underweight"]
bmi_dt[bmi >= 18.5 & bmi <= 24.9, bmi_class := "Normal Weight"]
bmi_dt[bmi >= 25 & bmi <= 29.9, bmi_class := "Overweight"]
bmi_dt[bmi >= 30, bmi_class := "Obese"]

ifps_subset_dt[bmi_dt, bmi := i.bmi_class, on = .(SAMPMIQ)]

rm(bmi_dt)
# ------------------------------------------------------------

# WIC Participation -------------------------------------------

wic_dt <- ifps_dt[, .(P6_1, P6_2, P6_3, SAMPMIQ)]

wic_dt[P6_1 == 1 | P6_2 == 1, wic_participation := TRUE]
wic_dt[P6_3 == 1, wic_participation := FALSE]

ifps_subset_dt[wic_dt, 
               wic_participation := i.wic_participation, 
               on = .(SAMPMIQ)]


rm(wic_dt)
# ----------------------------------------------------------------------

# Attitude toward breast feeding ----------------------------------

attitude_dt <- ifps_dt[, .(P35E, SAMPMIQ)]

attitude_dt[P35E == 1, breast_feeding_attitude := "Positive"]
attitude_dt[P35E %in% c(2:5), breast_feeding_attitude := "Negative"]

ifps_subset_dt[attitude_dt, 
               breast_feeding_attitude := i.breast_feeding_attitude, 
               on = .(SAMPMIQ)]


rm(attitude_dt)

# -----------------------------------------------------------------

```


```{r modeling, results = 'hide', echo = TRUE}
# Reshaping data before going into modeling
modeling_dt <- melt(ifps_subset_dt, 
                    measure.vars = paste0("breast_feeding_intensity_", 1:6, "_mo"), 
                      variable.name = "time_of_bf_intens_meas", 
                      value.name = "numeric_bf_intensity")

# Setting the boundaries for "low", "medium", and "high" breast feeding intensity
break_options <- c(0, .2, .8, 1)

modeling_dt[, breast_feeding_intensity := cut(numeric_bf_intensity,
                                                 breaks = break_options,
                                                 labels = c("Low", "Medium", "High"),
                                                 include.lowest = TRUE)]

# Perform chi-squared test

chi_sq_dt <- modeling_dt[!is.na(perception_of_support) &
                          !is.na(breast_feeding_intensity), .(breast_feeding_intensity,
                                                              perception_of_support,
                                                              time_of_bf_intens_meas)]

chi_sq_dt[, time_of_bf_intens_meas := gsub("breast_feeding_intensity_", "", 
                                             time_of_bf_intens_meas)]
chi_sq_dt[, time_of_bf_intens_meas := paste0(time_of_bf_intens_meas, "nth")]

chi_sq_test_list <- lapply(split(chi_sq_dt, by = "time_of_bf_intens_meas"), function(x){
  temp_table <- table(x$breast_feeding_intensity, x$perception_of_support)

  chi_sq_test <- chisq.test(temp_table)
  
  return(list(contingency_table = temp_table,
              chi_sq_test = chi_sq_test))
})


# Filtering down the dataset to mothers that had difficulties and support and responded
# with a perception of the support.  Also filtering out all rows that contain an NA
modeling_dt %<>% .[breast_feeding_difficulties == TRUE & 
                     breast_feeding_support == TRUE & 
                     !is.na(perception_of_support)] %>%
                na.omit()

modeling_dt[, numeric_bf_intensity := NULL]
modeling_dt[, time_of_bf_intens_meas := gsub("breast_feeding_intensity_", "", 
                                             time_of_bf_intens_meas)]
modeling_dt[, time_of_bf_intens_meas := paste0(time_of_bf_intens_meas, "nth")]

# Setting categorical variable columns to be 'factor' type in data for modeling
factor_cols <- modeling_dt[, .SD, .SDcols = -c("SAMPMIQ")] %>% colnames()

modeling_dt[, (factor_cols) := lapply(.SD, as.factor), .SDcols = factor_cols]

# Relevel Factors --------------------------------------------------------------

# Setting the reference level for all variables
modeling_dt[, `:=` (perception_of_support = relevel(perception_of_support, 
                                                    ref = "Inconclusive"),
                    breast_feeding_intensity = relevel(breast_feeding_intensity, 
                                                       ref = "Low"),
                    BFHI_score = relevel(BFHI_score, 
                                         ref = "0"),
                    maternal_age = relevel(maternal_age, 
                                           ref = "25-29"),
                    race_eth = relevel(race_eth, 
                                       ref = "White, Non-Hispanic"),
                    education = relevel(education, 
                                        ref = "High School"),
                    parity = relevel(parity, 
                                     ref = "primipara"),
                    income = relevel(income, 
                                     ref = "$20,000-$49,999"),
                    bmi = relevel(bmi, 
                                  ref = "Normal Weight"),
                    wic_participation = relevel(wic_participation, 
                                                ref = "FALSE"),
                    breast_feeding_attitude = relevel(breast_feeding_attitude, 
                                                      ref = "Negative"))]

base_levels <- lapply(modeling_dt, function(x){
  data.table(reference_level = levels(x)[1])
}) %>% rbindlist(., idcol = 'variable')
# ------------------------------------------------------------------------------

# List of datasets for 1-6 months to sequence along for modeling
modeling_data_list <- split(modeling_dt, by = "time_of_bf_intens_meas")

response_var <- "perception_of_support"

control_vars <- modeling_dt[, .SD, .SDcols = -c("SAMPMIQ", 
                                                "breast_feeding_difficulties", 
                                                "breast_feeding_support", 
                                                response_var,
                                                "breast_feeding_intensity",
                                                "time_of_bf_intens_meas")] %>% 
                colnames()

control_formula <- as.formula(paste("breast_feeding_intensity ~ ", 
                         paste(control_vars, collapse = "+")))

# Check for multi collinearity -------------------------------------------------
  # Computes multicollinearity diagnostic using generalized variance inflation
  # factors.  Metrics are computed for all control variables + perception of 
  # support
multi_col_model <- multinom(as.formula(paste("breast_feeding_intensity ~ ", 
                         paste(c(response_var, control_vars), collapse = "+"))),
                              data = modeling_dt[time_of_bf_intens_meas == "1_month"],
                              model = TRUE)
  
vif_dt <- vif(multi_col_model) %>% as.data.table()
vif_dt[, Variable := rownames(vif(multi_col_model))]
  

vif_dt[, `:=` (GVIF = round(GVIF, 2),
                     `GVIF^(1/(2*Df))` = round(`GVIF^(1/(2*Df))`, 2))]

fwrite(vif_dt, file.path(project.directory, "2_Outputs/Coefficient_Tables/vif_dt.csv"))
# -----------------------------------------------------

model_fit <- list()

# This loop fits a model at each month 1-6
for(i in seq_along(modeling_data_list)){

  temp_dt <- modeling_data_list[[i]]
  
  # Fits a regression model using all control variables
  temp_controlModel <- multinom(control_formula, data = temp_dt)
  
  # Applies stepwise regression to find an optimal control variable subset for 
  # the iteration
  temp_stepwiseModel <- stepAIC(temp_controlModel)
  
  optimal_control_variable_subset <- temp_stepwiseModel$xlevels %>% names()
  
  # Fits the full regression model using perception of support + optimized control
  # variables
  full_formula <- as.formula(paste("breast_feeding_intensity ~ ", 
                         paste(c(response_var, optimal_control_variable_subset), 
                               collapse = "+")))
  
  temp_fullModel <- multinom(full_formula, 
            data = temp_dt)
  
  # Create a table of variable coefficients and their associated odds ratios at 
  # different levels of the variable
  
   coef_dt <- coef(temp_fullModel) %>% as.data.table()

   coef_dt[, response_level := attributes(coef(temp_fullModel))$dimnames[[1]]]
  
   coef_dt %<>% melt(., id.vars = "response_level", variable.name = "variable", value.name = "coefficient")
  
   model_levels <- temp_fullModel$xlevels %>% 
    lapply(., as.data.table) %>% 
    rbindlist(., idcol = "variable")
  
   setnames(model_levels, "V1", "level")
  
   model_levels[, combined_name := paste0(variable, level)]
  
   coef_dt[model_levels, `:=` (variable_name = i.variable,
                              variable_level = i.level), on = .(variable = combined_name)]
   coef_dt[base_levels, reference_level := i.reference_level, on = .(variable_name = variable)]
  
   coef_dt %<>% .[!is.na(variable_name)]
  
   coef_dt[, rel_risk := exp(coefficient)]

   confint_dt <- confint(temp_fullModel) %>% as.data.table()

  confint_dt %<>% dcast(., ... ~ V2, value.var = "value")  

  setnames(confint_dt, c("variable", "response_level", "lower_log_rr_interval", "upper_log_rr_interval"))

  confint_dt[, `:=` (lower_rel_risk_interval = exp(lower_log_rr_interval),
                   upper_rel_risk_interval = exp(upper_log_rr_interval))]
  coef_dt <- merge(coef_dt,
                 confint_dt,
                 by = c("variable", "response_level"),
                        all.x = TRUE)

  coef_dt[, variable := NULL]
# Returns list of iteration results
  model_fit[[i]] <- list(full_model = temp_fullModel,
                         full_model_summary = summary(temp_fullModel),
       control_model = temp_stepwiseModel,
       stepwise_results = temp_stepwiseModel$anova,
       optimal_control_variables = optimal_control_variable_subset,
       likelihood_ratio_test = lrtest(temp_fullModel,
            temp_stepwiseModel),
       coef_dt = coef_dt)
}

names(model_fit) <- names(modeling_data_list)

saveRDS(model_fit, file.path(project.directory, "2_Outputs/R_Objects/model_fit.RDS"))

lapply(seq_along(model_fit), function(i){
  fwrite(model_fit[[i]]$coef_dt, 
         file.path(project.directory, 
                   paste0("2_Outputs/Coefficient_Tables/",
                          names(model_fit)[i],
                          "_model_coefficient_table.csv"))
  )
  
})

fwrite(modeling_dt, file.path(data.directory, "modeling_dt.csv"))
```



 \newpage
 
## Model Fit Summaries: Breast Feeding Intensity At Each Time Period

Modeling results are shown below.  For each month (1:6), a full and control model are fit,
according to the following structure.

$$\text{Full Model: Breast Feeding Intensty at }i_{th}\text{ Month}\sim\text{Perception of Support + Control Variables}$$

$$\text{Control Model: Breast Feeding Intensty at }i_{th}\text{ Month}\sim\text{Control Variables}$$

Each model is a **Multinomial Logistic Regression**.  The control variables to be used
are determined from a **bidirectional stepwise regression** using the Akaike Information Criterion.

Once the full and control models are fit, a likelihood ratio test is peformed between the two.  
The likelihood ratio test yields the following statistic:

${\displaystyle \lambda _{\text{LR}}=-2\ln \left[{\frac {~\sup _{\theta \in \Theta _{0}}{\mathcal {L}}(\theta )~}{~\sup _{\theta \in \Theta }{\mathcal {L}}(\theta )~}}\right]}$

According to Wilks' theorem, this statistic will asymptotically be chi-squared distributed 
(${\displaystyle \chi ^{2}}$) with degrees of freedom equal to the difference in dimensionality 
of ${\displaystyle \Theta }$  and ${\displaystyle \Theta _{0}}$

Leveraging this result, we can draw conclusions about the significance of perception
of support in predicting breast feeding intensity.

Multicollinearity between the predictors was measured through generalized variance
inflation factors (Cox and Monette Citation)


### 1 Month

The control variables determined are: `r model_fit[["1_month"]][["optimal_control_variables"]]`  

The likelihood ratio test is performed between the model fit with only the control variables (Control Model) 
and the model fit with both the control variables and perception of support (Full Model).  

The test statistic derived from the likelihood ratios of each model is: `r model_fit[["1_month"]][["likelihood_ratio_test"]][["Chisq"]][2]`  

This asymptotically approaches a chi-squared distribution with degrees of freedom: `r -model_fit[["1_month"]][["likelihood_ratio_test"]][["Df"]][2]`  

The sample size for this test is: `r modeling_data_list[["1_month"]][, .N]`  

This corresponds to a model p-value of: `r model_fit[["1_month"]][["likelihood_ratio_test"]][["Pr(>Chisq)"]][2]`  

#### Full Model

```{r}
model_fit[["1_month"]][["full_model"]]
```

#### Control Model

```{r}
model_fit[["1_month"]][["control_model"]]
```

#### Likelihood Ratio Test

```{r}
model_fit[["1_month"]][["likelihood_ratio_test"]]
```

### 2 Month

The control variables determined are: `r model_fit[["2_month"]][["optimal_control_variables"]]`  

The likelihood ratio test is performed between the model fit with only the control variables (Control Model) 
and the model fit with both the control variables and perception of support (Full Model).  

The test statistic derived from the likelihood ratios of each model is: `r model_fit[["2_month"]][["likelihood_ratio_test"]][["Chisq"]][2]`  

This asymptotically approaches a chi-squared distribution with degrees of freedom: `r -model_fit[["2_month"]][["likelihood_ratio_test"]][["Df"]][2]`  

The sample size for this test is: `r modeling_data_list[["2_month"]][, .N]`  

This corresponds to a model p-value of: `r model_fit[["2_month"]][["likelihood_ratio_test"]][["Pr(>Chisq)"]][2]`  

#### Full Model

```{r}
model_fit[["2_month"]][["full_model"]]
```

#### Control Model

```{r}
model_fit[["2_month"]][["control_model"]]
```

#### Likelihood Ratio Test

```{r}
model_fit[["2_month"]][["likelihood_ratio_test"]]
```

### 3 Month

The control variables determined are: `r model_fit[["3_month"]][["optimal_control_variables"]]`  

The likelihood ratio test is performed between the model fit with only the control variables (Control Model) 
and the model fit with both the control variables and perception of support (Full Model).  

The test statistic derived from the likelihood ratios of each model is: `r model_fit[["3_month"]][["likelihood_ratio_test"]][["Chisq"]][2]`  

This asymptotically approaches a chi-squared distribution with degrees of freedom: `r -model_fit[["3_month"]][["likelihood_ratio_test"]][["Df"]][2]`  

The sample size for this test is: `r modeling_data_list[["3_month"]][, .N]`  

This corresponds to a model p-value of: `r model_fit[["3_month"]][["likelihood_ratio_test"]][["Pr(>Chisq)"]][2]`  

#### Full Model

```{r}
model_fit[["3_month"]][["full_model"]]
```

#### Control Model

```{r}
model_fit[["3_month"]][["control_model"]]
```

#### Likelihood Ratio Test

```{r}
model_fit[["3_month"]][["likelihood_ratio_test"]]
```

### 4 Month

The control variables determined are: `r model_fit[["4_month"]][["optimal_control_variables"]]`  

The likelihood ratio test is performed between the model fit with only the control variables (Control Model) 
and the model fit with both the control variables and perception of support (Full Model).  

The test statistic derived from the likelihood ratios of each model is: `r model_fit[["4_month"]][["likelihood_ratio_test"]][["Chisq"]][2]`  

This asymptotically approaches a chi-squared distribution with degrees of freedom: `r -model_fit[["4_month"]][["likelihood_ratio_test"]][["Df"]][2]`  

The sample size for this test is: `r modeling_data_list[["4_month"]][, .N]`  

This corresponds to a model p-value of: `r model_fit[["4_month"]][["likelihood_ratio_test"]][["Pr(>Chisq)"]][2]`  

#### Full Model

```{r}
model_fit[["4_month"]][["full_model"]]
```

#### Control Model

```{r}
model_fit[["4_month"]][["control_model"]]
```

#### Likelihood Ratio Test

```{r}
model_fit[["4_month"]][["likelihood_ratio_test"]]
```

### 5 Month

The control variables determined are: `r model_fit[["5_month"]][["optimal_control_variables"]]`  

The likelihood ratio test is performed between the model fit with only the control variables (Control Model) 
and the model fit with both the control variables and perception of support (Full Model).  

The test statistic derived from the likelihood ratios of each model is: `r model_fit[["5_month"]][["likelihood_ratio_test"]][["Chisq"]][2]`  

This asymptotically approaches a chi-squared distribution with degrees of freedom: `r -model_fit[["5_month"]][["likelihood_ratio_test"]][["Df"]][2]`  

The sample size for this test is: `r modeling_data_list[["5_month"]][, .N]`  

This corresponds to a model p-value of: `r model_fit[["5_month"]][["likelihood_ratio_test"]][["Pr(>Chisq)"]][2]`  

#### Full Model

```{r}
model_fit[["5_month"]][["full_model"]]
```

#### Control Model

```{r}
model_fit[["5_month"]][["control_model"]]
```

#### Likelihood Ratio Test

```{r}
model_fit[["5_month"]][["likelihood_ratio_test"]]
```

### 6 Month

The control variables determined are: `r model_fit[["6_month"]][["optimal_control_variables"]]`  

The likelihood ratio test is performed between the model fit with only the control variables (Control Model) 
and the model fit with both the control variables and perception of support (Full Model).  

The test statistic derived from the likelihood ratios of each model is: `r model_fit[["6_month"]][["likelihood_ratio_test"]][["Chisq"]][2]`  

This asymptotically approaches a chi-squared distribution with degrees of freedom: `r -model_fit[["6_month"]][["likelihood_ratio_test"]][["Df"]][2]`  

The sample size for this test is: `r modeling_data_list[["6_month"]][, .N]`  

This corresponds to a model p-value of: `r model_fit[["6_month"]][["likelihood_ratio_test"]][["Pr(>Chisq)"]][2]`  

#### Full Model

```{r}
model_fit[["6_month"]][["full_model"]]
```

#### Control Model

```{r}
model_fit[["6_month"]][["control_model"]]
```

#### Likelihood Ratio Test

```{r}
model_fit[["6_month"]][["likelihood_ratio_test"]]
```