---
title: "ASSESSING THE IMPACT OF MOTHER’S PERCEPTION OF SUPPORT ON BREASTFEEDING INTENSITY THROUGH SIX MONTHS: STATISTICAL ANALYSIS"
author: "KATIE PALOMARES"
output:
  pdf_document:
    toc: yes
    toc_depth: 5
  html_document:
    toc: yes
    toc_depth: '5'
    df_print: paged
---

\newpage

## Data Prep

The code shown below implements the following process:

1. Read in full IFPS dataset
2. Subset the dataset to fields relevant to the study and apply necessary transformations
3. Fit a multinomial logistic regression model to the data in order to ascertain the significance
of perception of support on breast feeding intensity.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(haven)
library(data.table)
library(magrittr)
library(stats)
library(nnet)
library(lmtest)
library(MASS)
library(ggplot2)
```

```{r data_prep, results = 'hide', echo = TRUE}


data.directory <- "C:/Users/James/Documents/R/Katies_Thesis/0_Data/"

ifps_dt <- "ifps2.sas7bdat" %>%
           paste0(data.directory, .) %>%
           read_sas() %>%
           as.data.table()


modeling_dt <- ifps_dt[, .(SAMPMIQ)]

# Breastfeeding difficulties, question 36 --------------------------

N36_cols <- colnames(ifps_dt)[colnames(ifps_dt) %like% "N36"]

N36_dt <- melt(ifps_dt[, .SD, .SDcols = c("SAMPMIQ", N36_cols)], 
                id.vars = "SAMPMIQ", 
                value.name = "response", 
                variable.name = "question")

N36_dt %<>% .[, .(response = sum(response, na.rm = TRUE)), keyby = .(SAMPMIQ)]

N36_dt[, breast_feeding_difficulties := FALSE]
N36_dt[response > 0, breast_feeding_difficulties := TRUE]

modeling_dt[N36_dt, 
        breast_feeding_difficulties := i.breast_feeding_difficulties, 
        on = .(SAMPMIQ)]

rm(N36_dt, N36_cols)

# ----------------------------------------------------------------------

# Breast feeding support, question 38 -----------------------------------

N38_dt <- ifps_dt[, .(N38, SAMPMIQ)]
N38_dt[, breast_feeding_support := FALSE]
N38_dt[N38 == 1, breast_feeding_support := TRUE]

modeling_dt[N38_dt, 
            breast_feeding_support := i.breast_feeding_support, 
            on = .(SAMPMIQ)]

rm(N38_dt)

# ------------------------------------------------------------------------

# Perception of support, question 39

N39_dt <- ifps_dt[, .(N39, SAMPMIQ)]

N39_dt[N39 %in% c(1, 2), perception_of_support := "Unhelfpul"]
N39_dt[N39 %in% c(3), perception_of_support := "Inconclusive"]
N39_dt[N39 %in% c(4, 5), perception_of_support := "Helpful"]

modeling_dt[N39_dt, 
            perception_of_support := i.perception_of_support, 
            on = .(SAMPMIQ)]

rm(N39_dt)

# -----------------------------------------------------------------------

# Breast Feeding Intensity at 2 - 6 months ----------------------------

months <- 1:6

for(i in months){
  
  if (i == 1) {
    feeding_cols <- colnames(ifps_dt)[colnames(ifps_dt) %like% "N40"]
    
    bf_feeding_col <- "N40A"
  } else {
    feeding_cols <- paste0("M", i, "A1", LETTERS[1:10])
    
    bf_feeding_col <- paste0("M", i, "A1A")
  }

  
  temp_dt <- melt(ifps_dt[, .SD, .SDcols = c("SAMPMIQ", feeding_cols)],
                  id.vars = "SAMPMIQ",
                  value.name = "response",
                  variable.name = "question")
  
  temp_dt[is.na(response) & question == bf_feeding_col, response := 0]
  
  temp_dt %<>% .[, .(breast_feeding_intensity = response[question == bf_feeding_col]/sum(response, 
                                                                                     na.rm = TRUE)), 
                keyby = .(SAMPMIQ)]
  
  temp_dt[is.nan(breast_feeding_intensity), breast_feeding_intensity := NA]
  
  modeling_dt[temp_dt, breast_feeding_intensity := i.breast_feeding_intensity, on = .(SAMPMIQ)]
  
  setnames(modeling_dt, "breast_feeding_intensity", paste0("breast_feeding_intensity_", i, "_mo"))
  
  rm(feeding_cols, bf_feeding_col, temp_dt)
}

# ----------------------------------------------------------------------

# BFHI Exposure --------------------------------------------------------

BFHI_dt <- ifps_dt[, .SD, .SDcols = c("N20", 
                                      "N11", 
                                      "N25", 
                                      "N28", 
                                      paste0("N29", c("A", "B", "C")),
                                      "N32", 
                                      "SAMPMIQ")]

number_BFHI_criteria <- 6

# Time until mother breastfed for the first time
BFHI_dt[N20 %in% 1:2, BFHI_exp_1 := TRUE]
BFHI_dt[N20 %in% 3:9, BFHI_exp_1 := FALSE]

# No Pacifiers
BFHI_dt[N11 %in% c(1, 3), BFHI_exp_2 := FALSE]
BFHI_dt[N11 %in% c(2), BFHI_exp_2 := TRUE]

# Rooming in
BFHI_dt[N25 %in% c(1), BFHI_exp_3 := TRUE]
BFHI_dt[N25 %in% c(2, 3), BFHI_exp_3 := FALSE]

# BF on Demand
BFHI_dt[N28 %in% c(1), BFHI_exp_4 := TRUE]
BFHI_dt[N28 %in% c(2, 3), BFHI_exp_4 := FALSE]

# Only BM
BFHI_dt[N29A == 2 & N29B == 2 & N29C == 2, BFHI_exp_5 := TRUE]
BFHI_dt[N29A %in% c(1, 3) | N29B %in% c(1, 3) | N29C %in% c(1, 3), BFHI_exp_5 := FALSE]

# Fostering support groups
BFHI_dt[N32 == 1, BFHI_exp_6 := TRUE]
BFHI_dt[N32 == 2, BFHI_exp_6 := FALSE]

BFHI_dt %<>% melt(., measure.vars = paste0("BFHI_exp_", 1:number_BFHI_criteria),
                  variable.name = "question",
                  value.name = "response")

BFHI_dt %<>% .[, .(BFHI_score = sum(response, na.rm = TRUE),
                   BFHI_all_missing = all(is.na(response))), by = .(SAMPMIQ)]

BFHI_dt[BFHI_all_missing == TRUE, BFHI_score := NA]

modeling_dt[BFHI_dt, BFHI_score := i.BFHI_score, on = .(SAMPMIQ)]

rm(BFHI_dt, number_BFHI_criteria)
# ----------------------------------------------------------------------

# Maternal Age ---------------------------------------------------------
P9_dt <- ifps_dt[, .(P9, SAMPMIQ)]

P9_dt[, unique(P9)] %>% sort()

P9_dt[, maternal_age := cut(P9, 
                            breaks = c(18, 25, 30, 35, Inf), 
                            labels = c("18-24", "25-29", "30-34", "35+"),
                            include.lowest = TRUE,
                            right = FALSE)]

modeling_dt[P9_dt, maternal_age := i.maternal_age, on = .(SAMPMIQ)]

rm(P9_dt)
# ----------------------------------------------------------------------

# Race/Ethnicity -------------------------------------------------------

race_dt <- ifps_dt[, .(RACE_ETH, SAMPMIQ)]

race_dt[RACE_ETH == 1, race_eth := "White, Non-Hispanic"]
race_dt[RACE_ETH == 2, race_eth := "Black, Non-Hispanic"]
race_dt[RACE_ETH == 3, race_eth := "Hispanic"]
race_dt[RACE_ETH %in% c(4, 5), race_eth := "Other"]

modeling_dt[race_dt, race_eth := i.race_eth, on = .(SAMPMIQ)]

rm(race_dt)
# ----------------------------------------------------------------------

# Education ---------------------------------------------
edu_dt <- ifps_dt[, .(EDUC, SAMPMIQ)]

edu_dt[EDUC %in% c(1, 2, 3), education := "Less Than High School"]
edu_dt[EDUC %in% c(4), education := "High School"]
edu_dt[EDUC %in% c(5), education := "1-3 Years College"]
edu_dt[EDUC %in% c(6, 7), education := "College Graduate"]

modeling_dt[edu_dt, education := i.education, on = .(SAMPMIQ)]

rm(edu_dt)
# -------------------------------------------------------

# Parity ------------------------------------------------
parity_dt <- ifps_dt[, .(P41_1, P41_2, SAMPMIQ)]

parity_dt[P41_1 == 0 & P41_2 == 0, parity := "nullipara"]
parity_dt[P41_1 %in% 1:12 | P41_2 %in% 1:12, parity := "primipara"]

modeling_dt[parity_dt, parity := i.parity, on = .(SAMPMIQ)]

parity_dt[, .N, by = .(keyby = P41_1)]
parity_dt[, .N, by = .(keyby = P41_2)]
rm(parity_dt)
# -------------------------------------------------------

# Income Level --------------------------------------------

income_dt <- ifps_dt[, .(INCOME, SAMPMIQ)]

income_dt[INCOME %in% 31:37, income := "<$20,000"]
income_dt[INCOME %in% 38:46, income := "$20,000-$49,999"]
income_dt[INCOME %in% 47:57, income := ">$50,000"]

modeling_dt[income_dt, income := i.income, on = .(SAMPMIQ)]

rm(income_dt)
# ---------------------------------------------------------

# BMI -----------------------------------------------------
bmi_dt <- ifps_dt[, .(P7, P8FT, P8IN, SAMPMIQ)]

bmi_dt[, bmi := (P7/((P8FT * 12 + P8IN)^2)) * 703]

bmi_dt[bmi < 18.5, bmi_class := "Underweight"]
bmi_dt[bmi >= 18.5 & bmi <= 24.9, bmi_class := "Normal Weight"]
bmi_dt[bmi >= 25 & bmi <= 29.9, bmi_class := "Overweight"]
bmi_dt[bmi >= 30, bmi_class := "Obese"]

modeling_dt[bmi_dt, bmi := i.bmi_class, on = .(SAMPMIQ)]

rm(bmi_dt)
# ------------------------------------------------------------

# WIC Participation -------------------------------------------

wic_dt <- ifps_dt[, .(P6_1, P6_2, P6_3, SAMPMIQ)]

wic_dt[P6_1 == 1 | P6_2 == 1, wic_participation := TRUE]
wic_dt[P6_3 == 1, wic_participation := FALSE]

modeling_dt[wic_dt, wic_participation := i.wic_participation, on = .(SAMPMIQ)]


rm(wic_dt)
# ----------------------------------------------------------------------

# Attitude toward breast feeding ----------------------------------

attitude_dt <- ifps_dt[, .(P35E, SAMPMIQ)]

attitude_dt[P35E == 1, breast_feeding_attitude := "Positive"]
attitude_dt[P35E %in% c(2:5), breast_feeding_attitude := "Negative"]

modeling_dt[attitude_dt, breast_feeding_attitude := i.breast_feeding_attitude, on = .(SAMPMIQ)]


rm(attitude_dt)

# -----------------------------------------------------------------

# Modeling -------------------------------------------------------------

modeling_cols <- paste0("bf_intens_", 1:6, "_mo")

break_options <- c(0, .2, .8, 1)
# break_options <- c(0, .25, .75, 1)

modeling_dt[, (modeling_cols) := lapply(.SD, 
                                        cut, 
                                        breaks = break_options,
                                        labels = c("Low", "Medium", "High"),
                                        include.lowest = TRUE), 
            .SDcols = paste0("breast_feeding_intensity_", 1:6, "_mo")]

modeling_dt[, (paste0("breast_feeding_intensity_", 1:6, "_mo")) := NULL]

modeling_dt %<>% .[breast_feeding_difficulties == TRUE & 
                     breast_feeding_support == TRUE & 
                     !is.na(perception_of_support)]

setnames(modeling_dt, modeling_cols, paste0(1:6, "_month"))

modeling_dt %<>% melt(., measure.vars = paste0(1:6, "_month"), 
                      variable.name = "time_of_bf_intens_meas", 
                      value.name = "breast_feeding_intensity")

# modeling_dt %<>% .[!is.na(breast_feeding_intensity)]
modeling_dt %<>% na.omit(.)

factor_cols <- modeling_dt[, .SD, .SDcols = -c("SAMPMIQ")] %>% colnames()

modeling_dt[, (factor_cols) := lapply(.SD, as.factor), .SDcols = factor_cols]



```

```{r modeling, results = 'hide', echo = TRUE}
# Relevel Factors --------------------------------------------------------------

modeling_dt[, `:=` (perception_of_support = relevel(perception_of_support, ref = "Inconclusive"),
                    breast_feeding_intensity = relevel(breast_feeding_intensity, ref = "Low"))]
# ------------------------------------------------------------------------------

modeling_data_list <- split(modeling_dt, by = "time_of_bf_intens_meas")

response_var <- "perception_of_support"

control_vars <- modeling_dt[, .SD, .SDcols = -c("SAMPMIQ", 
                                                "breast_feeding_difficulties", 
                                                "breast_feeding_support", 
                                                response_var,
                                                "breast_feeding_intensity",
                                                "time_of_bf_intens_meas")] %>% colnames()

control_formula <- as.formula(paste("breast_feeding_intensity ~ ", 
                         paste(control_vars, collapse = "+")))

univariate_fits <- list()

 for(i in seq_along(modeling_data_list)){
      temp_dt <- modeling_data_list[[i]]
  temp_model_list <- lapply(control_vars, function(y){
    
    temp_formula <- as.formula(paste0("breast_feeding_intensity ~ ", y))
    temp_model <- multinom(temp_formula, data = temp_dt)
    temp_lr_test <- lrtest(temp_model)
    
    return(list(univariate_model = temp_model, 
                likelihood_ratio_test = temp_lr_test))
  })
  
  names(temp_model_list) <- control_vars
  
  univariate_fits[[i]] <- temp_model_list
 }

names(univariate_fits) <- names(modeling_data_list)

# -----------------------------------------------------

model_fit <- list()

for(i in seq_along(modeling_data_list)){

  temp_dt <- modeling_data_list[[i]]
  
  temp_controlModel <- multinom(control_formula, data = temp_dt)
  
  temp_stepwiseModel <- stepAIC(temp_controlModel)
  
  optimal_control_variable_subset <- temp_stepwiseModel$xlevels %>% names()
  
  
full_formula <- as.formula(paste("breast_feeding_intensity ~ ", 
                         paste(c(response_var, optimal_control_variable_subset), collapse = "+")))
  
  temp_fullModel <- multinom(full_formula, 
            data = temp_dt)
  
  aic_table <- data.table(Model = c("Full_Model",
                                    "Control_Model"),
                          AIC = c(temp_fullModel$AIC, temp_controlModel$AIC),
                          Relative_Likelihood = c(exp(-abs(temp_fullModel$AIC - temp_controlModel$AIC)/2),
                                                  NA))
  model_fit[[i]] <- list(full_model = temp_fullModel,
       control_model = temp_stepwiseModel,
       stepwise_results = temp_stepwiseModel$anova,
       optimal_control_variables = optimal_control_variable_subset,
       likelihood_ratio_test = lrtest(temp_fullModel,
            temp_stepwiseModel),
       AIC_table = aic_table)
}

names(model_fit) <- names(modeling_data_list)
# Plots -----------------------------------------------------------

dist_plot <- ggplot(modeling_dt, aes(x = breast_feeding_intensity, fill = perception_of_support)) +
  geom_bar(stat = "count", position = "dodge") +
  facet_wrap(~ time_of_bf_intens_meas, ncol = 2)
# ----------------------------------------------------------------------

```

 \newpage
 
## Model Fit Summaries: Breast Feeding Intensity At Each Time Period

Modeling results are shown below.  For each month (1:6), a full and control model are fit,
according to the following structure.

$$\text{Full Model: Breast Feeding Intensty at }i_{th}\text{ Month}\sim\text{Perception of Support + Control Variables}$$

$$\text{Control Model: Breast Feeding Intensty at }i_{th}\text{ Month}\sim\text{Control Variables}$$

Each model is a **Multinomial Logistic Regression**.  The control variables to be used
are determined from a **bidirectional stepwise regression** using the Akaike Information Criterion.

Once the full and control models are fit, a likelihood ratio test is peformed between the two.  
The likelihood ratio test yields the following statistic:

${\displaystyle \lambda _{\text{LR}}=-2\ln \left[{\frac {~\sup _{\theta \in \Theta _{0}}{\mathcal {L}}(\theta )~}{~\sup _{\theta \in \Theta }{\mathcal {L}}(\theta )~}}\right]}$

According to Wilks' theorem, this statistic will asymptotically be chi-squared distributed 
(${\displaystyle \chi ^{2}}$) with degrees of freedom equal to the difference in dimensionality 
of ${\displaystyle \Theta }$  and ${\displaystyle \Theta _{0}}$

Leveraging this result, we can draw conclusions about the significance of perception
of support in predicting breast feeding intensity.


### 1 Month

The control variables determined are: `r model_fit[["1_month"]][["optimal_control_variables"]]`  

The likelihood ratio test is performed between the model fit with only the control variables (Control Model) 
and the model fit with both the control variables and perception of support (Full Model).  

The test statistic derived from the likelihood ratios of each model is: `r model_fit[["1_month"]][["likelihood_ratio_test"]][["Chisq"]][2]`  

This asymptotically approaches a chi-squared distribution with degrees of freedom: `r -model_fit[["1_month"]][["likelihood_ratio_test"]][["Df"]][2]`  

The sample size for this test is: `r modeling_data_list[["1_month"]][, .N]`  

This corresponds to a model p-value of: `r model_fit[["1_month"]][["likelihood_ratio_test"]][["Pr(>Chisq)"]][2]`  

#### Full Model

```{r}
model_fit[["1_month"]][["full_model"]]
```

#### Control Model

```{r}
model_fit[["1_month"]][["control_model"]]
```

#### Likelihood Ratio Test

```{r}
model_fit[["1_month"]][["likelihood_ratio_test"]]
```

### 2 Month

The control variables determined are: `r model_fit[["2_month"]][["optimal_control_variables"]]`  

The likelihood ratio test is performed between the model fit with only the control variables (Control Model) 
and the model fit with both the control variables and perception of support (Full Model).  

The test statistic derived from the likelihood ratios of each model is: `r model_fit[["2_month"]][["likelihood_ratio_test"]][["Chisq"]][2]`  

This asymptotically approaches a chi-squared distribution with degrees of freedom: `r -model_fit[["2_month"]][["likelihood_ratio_test"]][["Df"]][2]`  

The sample size for this test is: `r modeling_data_list[["2_month"]][, .N]`  

This corresponds to a model p-value of: `r model_fit[["2_month"]][["likelihood_ratio_test"]][["Pr(>Chisq)"]][2]`  

#### Full Model

```{r}
model_fit[["2_month"]][["full_model"]]
```

#### Control Model

```{r}
model_fit[["2_month"]][["control_model"]]
```

#### Likelihood Ratio Test

```{r}
model_fit[["2_month"]][["likelihood_ratio_test"]]
```

### 3 Month

The control variables determined are: `r model_fit[["3_month"]][["optimal_control_variables"]]`  

The likelihood ratio test is performed between the model fit with only the control variables (Control Model) 
and the model fit with both the control variables and perception of support (Full Model).  

The test statistic derived from the likelihood ratios of each model is: `r model_fit[["3_month"]][["likelihood_ratio_test"]][["Chisq"]][2]`  

This asymptotically approaches a chi-squared distribution with degrees of freedom: `r -model_fit[["3_month"]][["likelihood_ratio_test"]][["Df"]][2]`  

The sample size for this test is: `r modeling_data_list[["3_month"]][, .N]`  

This corresponds to a model p-value of: `r model_fit[["3_month"]][["likelihood_ratio_test"]][["Pr(>Chisq)"]][2]`  

#### Full Model

```{r}
model_fit[["3_month"]][["full_model"]]
```

#### Control Model

```{r}
model_fit[["3_month"]][["control_model"]]
```

#### Likelihood Ratio Test

```{r}
model_fit[["3_month"]][["likelihood_ratio_test"]]
```

### 4 Month

The control variables determined are: `r model_fit[["4_month"]][["optimal_control_variables"]]`  

The likelihood ratio test is performed between the model fit with only the control variables (Control Model) 
and the model fit with both the control variables and perception of support (Full Model).  

The test statistic derived from the likelihood ratios of each model is: `r model_fit[["4_month"]][["likelihood_ratio_test"]][["Chisq"]][2]`  

This asymptotically approaches a chi-squared distribution with degrees of freedom: `r -model_fit[["4_month"]][["likelihood_ratio_test"]][["Df"]][2]`  

The sample size for this test is: `r modeling_data_list[["4_month"]][, .N]`  

This corresponds to a model p-value of: `r model_fit[["4_month"]][["likelihood_ratio_test"]][["Pr(>Chisq)"]][2]`  

#### Full Model

```{r}
model_fit[["4_month"]][["full_model"]]
```

#### Control Model

```{r}
model_fit[["4_month"]][["control_model"]]
```

#### Likelihood Ratio Test

```{r}
model_fit[["4_month"]][["likelihood_ratio_test"]]
```

### 5 Month

The control variables determined are: `r model_fit[["5_month"]][["optimal_control_variables"]]`  

The likelihood ratio test is performed between the model fit with only the control variables (Control Model) 
and the model fit with both the control variables and perception of support (Full Model).  

The test statistic derived from the likelihood ratios of each model is: `r model_fit[["5_month"]][["likelihood_ratio_test"]][["Chisq"]][2]`  

This asymptotically approaches a chi-squared distribution with degrees of freedom: `r -model_fit[["5_month"]][["likelihood_ratio_test"]][["Df"]][2]`  

The sample size for this test is: `r modeling_data_list[["5_month"]][, .N]`  

This corresponds to a model p-value of: `r model_fit[["5_month"]][["likelihood_ratio_test"]][["Pr(>Chisq)"]][2]`  

#### Full Model

```{r}
model_fit[["5_month"]][["full_model"]]
```

#### Control Model

```{r}
model_fit[["5_month"]][["control_model"]]
```

#### Likelihood Ratio Test

```{r}
model_fit[["5_month"]][["likelihood_ratio_test"]]
```

### 6 Month

The control variables determined are: `r model_fit[["6_month"]][["optimal_control_variables"]]`  

The likelihood ratio test is performed between the model fit with only the control variables (Control Model) 
and the model fit with both the control variables and perception of support (Full Model).  

The test statistic derived from the likelihood ratios of each model is: `r model_fit[["6_month"]][["likelihood_ratio_test"]][["Chisq"]][2]`  

This asymptotically approaches a chi-squared distribution with degrees of freedom: `r -model_fit[["6_month"]][["likelihood_ratio_test"]][["Df"]][2]`  

The sample size for this test is: `r modeling_data_list[["6_month"]][, .N]`  

This corresponds to a model p-value of: `r model_fit[["6_month"]][["likelihood_ratio_test"]][["Pr(>Chisq)"]][2]`  

#### Full Model

```{r}
model_fit[["6_month"]][["full_model"]]
```

#### Control Model

```{r}
model_fit[["6_month"]][["control_model"]]
```

#### Likelihood Ratio Test

```{r}
model_fit[["6_month"]][["likelihood_ratio_test"]]
```